{\plant}: A package for modelling forest trait ecology \& evolution

### 2015-06-01 ms.tex
No conflicts of interest
Work around manuscript central :fire::fire:

\newcommand{\plant}{\texttt{plant}}
\usepackage{graphicx}

@@

DS Falster was supported by an Australian Research Council (ARC)
discovery grant (DP110102086). RG FitzJohn was supported by the
Science and Industry Endowment Fund (RP04-174). M Westoby was
supported by a fellowship from the ARC. We thank {\AA}
Br{\"a}nnstr{\"o}m, J Camac, A De Roos, U Dieckmann, R Duursma, J
Johansson and C Prentice for helpful discussions.

@@

See attached file \url{vignettes/plant.pdf}, knitr source
\url{vignettes/plant.Rmd}, plain source, \url{vignettes/R/plant.R}

@@

See attached file \url{vignettes/cohort_spacing.pdf}, knitr source
\url{vignettes/cohort_spacing.Rmd}, plain source, \url{vignettes/R/cohort_spacing.R}

@@

See attached file \url{vignettes/equilibrium.pdf}, knitr source
\url{vignettes/equilibrium.Rmd}, plain source, \url{vignettes/R/equilibrium.R}

@@

See attached file \url{vignettes/patch.pdf}, knitr source
\url{vignettes/patch.Rmd}, plain source, \url{vignettes/R/patch.R}

@@

See attached file \url{vignettes/emergent.pdf}, knitr source
\url{vignettes/emergent.Rmd}, plain source, \url{vignettes/R/emergent.R}

@@

See attached file \url{vignettes/fitness.pdf}, knitr source
\url{vignettes/fitness.Rmd}, plain source, \url{vignettes/R/fitness.R}

\section{Modifying parameters of the physiological model}\label{sec:parameters}

See attached file \url{vignettes/parameters.pdf}, knitr source
\url{vignettes/parameters.Rmd}, plain source, \url{vignettes/R/parameters.R}

>>>>

\newcommand{\plant}{\texttt{plant}}
\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
\usepackage{graphicx}

@@

DS Falster was supported by an Australian Research Council (ARC)
discovery grant (DP110102086). RG FitzJohn was supported by the
Science and Industry Endowment Fund (RP04-174). M Westoby was
supported by a fellowship from the ARC. We thank {\AA}
Br{\"a}nnstr{\"o}m, J Camac, A De Roos, U Dieckmann, R Duursma, J
Johansson and C Prentice for helpful discussions. The authors have no 
conflicts of interest to declare.

@@

\emph{Note}: due to Manuscript Central not accepting \textsc{html}
files, we have had to convert this (and the following appendices) to
\textsc{pdf}s.  \textsc{html} versions are available on the wiki:
https://github.com/traitecoevo/plant\_paper/wiki --- the \textsc{html}
versions have less pixelated graphics and are easier to copy and
paste out of.

See attached file \url{vignettes/plant.pdf}, 
source:
\smurl{https://github.com/traitecoevo/plant\_paper/blob/master/vignettes/src/plant.R}
html: \smurl{https://github.com/traitecoevo/plant\_paper/wiki/plant}

@@

See attached file \url{vignettes/cohort_spacing.pdf},
source:
\smurl{https://github.com/traitecoevo/plant\_paper/blob/master/vignettes/src/cohort_spacing.R}
html: \smurl{https://github.com/traitecoevo/plant\_paper/wiki/cohort_spacing}

@@

See attached file \url{vignettes/equilibrium.pdf}
source:
\smurl{https://github.com/traitecoevo/plant\_paper/blob/master/vignettes/src/equilibrium.R}
html: \smurl{https://github.com/traitecoevo/plant\_paper/wiki/equilibrium}

@@

See attached file \url{vignettes/patch.pdf}
source:
\smurl{https://github.com/traitecoevo/plant\_paper/blob/master/vignettes/src/patch.R}
html: \smurl{https://github.com/traitecoevo/plant\_paper/wiki/patch}

@@

See attached file \url{vignettes/emergent.pdf}
source:
\smurl{https://github.com/traitecoevo/plant\_paper/blob/master/vignettes/src/emergent.R}
html: \smurl{https://github.com/traitecoevo/plant\_paper/wiki/emergent}

@@

See attached file \url{vignettes/fitness.pdf}
source:
\smurl{https://github.com/traitecoevo/plant\_paper/blob/master/vignettes/src/fitness.R}
html: \smurl{https://github.com/traitecoevo/plant\_paper/wiki/fitness}

\section{Modifying parameters of the physiological model}\label{sec:parameters}
See attached file \url{vignettes/parameters.pdf}
source:
\smurl{https://github.com/traitecoevo/plant\_paper/blob/master/vignettes/src/parameters.R}
html: \smurl{https://github.com/traitecoevo/plant\_paper/wiki/parameters}
